# Data Description

```{r message=FALSE, warning=FALSE, include=FALSE}
library(lemon)
knit_print.table <- lemon_print
```


The data contains the 196 observations and 5 variables including the following depicted in Figure \@ref(fig:fig1). 

```{r fig1, echo = F, fig.cap = 'Data Structure'}
library(png)
library(grid)
img <- readPNG("./pictures/figure1.png")
grid.raster(img)
```


The variable class represents the status of the legislative text in the congresional roll call, either 0 or 1. A 0 reflects failure and a 1 is defined as a pass. 
The voting responses are a character type including the following responses when collected from original source yea, nay, aye, no, and not voting. 
We convert the original source data to a binary response to capture the features detailed below.
The classes of the data are an equal distribution of representation as in Table \@ref(tab:confusion).

```{r confusion, echo = F}
best.cm <- data.frame(cbind(c(98),c(98)))
colnames(best.cm) = c("0", "1")
knitr::kable(
  best.cm,
  booktabs = TRUE,
  caption = 'Equal Distribution of Classes'
)
```

In section \@ref(method-and-materials) the process to create the proper label is detailed. 
The path includes the source folder of the legislative text. 
The path communicates the number of the congress, the year, and the unique id for each vote as depicted in Figure \@ref(fig:fig2). 

```{r fig2, echo = F, fig.cap = 'Sample of Path Title'}
library(png)
library(grid)
img <- readPNG("./pictures/figure3.png")
grid.raster(img)
```


The data also includes the pre-processed texts. 
In section \@ref(method-and-materials) the process to create the preprocessed text is detailed. 
In Figure \@ref(fig:fig3) a sample of the text is shown. Converting the preprocessed text into a document term matrix (DTM) provides the number of unique words in the sample.
Refer to Figure \@ref(fig:fig4).
The DTM also provides insight into the non-/sparse entries from the sample with a ratio of `r 151158/3496402`. 
The maximum term length results in only 44, indicating that some very large character sequences are contained in the text. 
A large number of terms represented in the language expresses the complexity of the content contained in the legislative text.

```{r fig3, echo = F, fig.cap = 'Sample of Preprocessed Text'}
library(png)
library(grid)
img <- readPNG("./pictures/figure4.png")
grid.raster(img)
```

```{r fig4, echo = F, fig.cap = 'Document Term Matrix of Preprocessed Text'}
library(png)
library(grid)
img <- readPNG("./pictures/figure7.png")
grid.raster(img)
```

The next variable contained in the data is the document id for each text samples. 
The document id serves as an easier identifier for  the samples then the path title. 
The unique identifiers are numerical values, 1:196. 

The final variable in the dataframe is an annotated and reshaped text paired with parts of speech. 
In Figure  \@ref(fig:fig5) a sample of the manipulated text is depicted. 

```{r fig5, echo = F, fig.cap = 'Preprocessed Text paired with parts of speech'}
library(png)
library(grid)
img <- readPNG("./pictures/figure6.png")
grid.raster(img)
```

The complete process to collect and reshape the data is discussed in the Section \@ref(method-and-materials). 